Vulnerability Analysis of Container Images in Neuroimaging

### 2020-02-14 paper.tex
after grammer check

Tools that are capable of packing and running an application in an isolated environment
are known as container tools. Alongwith an application they also pack the application's dependencies,
required libraries and configuration files for the
application to function properly. The functioning of an application in an isolated environment
is called a container. Containers directly run on the Host machine's kernel so they are lightweight.
Consequently, more containers can be run on a given Host machine as compared to virtual machines.

@@

\textit{Docker Daemon:} It acts as a server. It is
a long running process that manages all Docker images, containers, storage volumes, and networks.

\textit{REST API:} It acts as a interface between the server and the client, and is an API which is used by the applications
to talk to the \textit{Docker Daemon}.

@@

\begin{comment}
It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc.
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. 
\end{comment}
As Docker users directly interact with the
Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
???BLOCK MISSING

@@

Singularity is another tool for packing and running applications in containers. 
In our experiments, we used $2.5.2$ Singularity version. 
\begin{comment}
Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.
\end{comment}

@@

A container image is a package that contains an application along with its
required dependencies and libraries.
Both, Docker and Singularity, have different image formats. Below we provide description of both image
formats.

@@

On the other hand, Singularity image is a single immutable file and 
does not contain layers.
\begin{comment}
Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.

\subsection{Application frameworks}

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because one of them was not available
on Docker hub.

@@

Boutiques~\cite{glatard2018boutiques} is a application sharing system to
publish, integrate, and execute command-line applications across different
platforms. In Boutiques, the command-line of the application is described
through a flexible JSON descriptor pointing to a Docker or a Singularity
image where the application is installed. A set of core tools help
construct, validate, publish and execute Boutiques descriptors. Boutiques
applications are published on the Zenodo research repository.

We used the 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images. Out of these images,
3 images are not found and 2 images were already included in BIDS images.
Therefore we are left with total 18 Boutiques images which includes 6
Singularity images and 12 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because QAP bids app was not available
on Docker hub.

So we have total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

BIDS app and Boutiques images that we took for our experiment have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. In case of Ubuntu, release
can be of two types : regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

Scanning an image means looking into the image, collecting all the information about the image, and
finally, using this information to detect vulnerabilities present inside the image.
Scanning can be broadly categorised into two types: \rom{1} Static Scanning and \rom{2}
Dynamic Scanning.
In Static scanning, an image is scanned without running it into a container. In respect to that,
differnt image features are extracted like installed packages, their versions, files, etc.
On the other hand, Dynamic scanning involves running a container from the image and then scanning the
dynamic behaviour of the image.

@@

We used three scanners namely Anchore~\cite{github_2019}, Vuls~\cite{future-architect_2019}, and
Clair Scanner~\cite{arminc_2019} for scanning Docker images because these are the most
mature scanners. Out of these scanners, only Vuls uses dynamic scanning and remaining two
are static scanners.
Also, we freezed vulnerability databases for these scanners on September 25, 2019 and scanned
all images to avoid getting different results due to the differences in the scanner's database.
Lastly, for scanning Singularity images, we used Stools.

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get vulnerability feed of various OS distribution, Anchore refers to
different sources. For example Ubuntu launchpad database is used for Ubuntu.
In Ubuntu launchpad database, for a given CVE, there is entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in following form:
\newline \\

@@

The status can be anyone of the following:

@@

\textbf{not-affected:} The package (inside the given release), while related to the
		CVE in some way, is not affected by the issue. Notes should
		provide detailed information, if needed. For e.g
		"not-affected (1.14.6-1.1)" indicates that this specific
		package version in the given release is not affected.

@@

\textbf{ignored:} The package (inside the given release), while related to the
		CVE in some way, is being ignored for some reason.  The
		notes should provide that reason. For e.g "ignored (reached end-of-life)".
		This means that this given Ubuntu release already reached
		end-of-life so this CVE is ignored by Ubuntu. However, if there
		is an extended security support for this release then this
		CVE will be handled in ESM release.

\textbf{pending:} The package (inside the given release) is vulnerable, and
                  has been fixed but an update has not been yet uploaded or
		  pushlished. The "version" indicates the package version 
		  that contains the fix.

@@

Figure~\ref{example} illustrates how the information of a CVE is represented
in Ubuntu launchpad database.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using dynamic scanning technique, it offers
remote and local scan. Remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer fast scan, fast root scan,
and deep scan.
Fast scan is performed without root privileges, whereas fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. Deep scan uses
root privileges for scanning, and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registery to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide facility of comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose a Docker image is maintained that contains Ubuntu CVE tracker database.
Whenever Ubuntu updated its database, this image is also updated with the required information.

@@

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intented to scan Docker Containers. This tool does not fit well
to scan Singularity images because of the different image formats. Docker images
consist of layers, whereas Singluarity images consist of a single binary file.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks
package manager present inside the image and then according to that it
updates the image. However, this option effects the reproducibility
of the image, which means that the image cannot be used to verify research
findings of other scientists.

@@

In this section, we present and compare scanning results of three scanners.

@@

Figure~\ref{fig:venn} illustrates the number of vulnerabilities detected by scanners. The
overlapping regions of Venn diagram shows the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner.

Figure~\ref{fig:graph1} gives more image specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Cnetos contain higher number of critical vulnerabilities than Ubuntu and Alpine.

@@

Table~\ref{table1} compares results of scanning images with the three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table.

When we add all regions of Venn diagram
we get total 20050 vulnerabilities in Bids and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 only reported by Clair, and 325 only detected by Vuls.
libavlibavlibavlibavlibavlibavlibav
The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
The question arises why these scanners report different number and type of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.

According to our investigation of these results, below are some of the reasons of
getting different results from these scanners. These reasons include bugs in scanners,
some scanners ignoring vulnerabilities in a particular package, referring to different databases,
how frequently they are updating their databases, etc.

@@

\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports them.
4443 out of 4453 vulnerabilities that are only reported by Anchore are present in linux-kernel-headers.
For example CVE-2019-9506 present in linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair Scanner.

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities with status
as "not-affected". So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls. In other words, we can say that
these are false positives by Vuls.
For example, we scanned an image having Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
is not affected by this CVE.

\textbf{With CVE status as "Ignored (reached end-of-life)":}
Some vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
only refers ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE", which means does not exist, then Clair Scanner will not report it. 
For example CVE-2017-9994 vulnerability in libav package is ignored in Trusty LTS release due end-of-life.
so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
release so Clair Scanner also do not report it. As Ubuntu 14.04 LTS release is present inside the images still
Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.

@@

\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
is present in package cairo in Xenial release and it is not detected by Clair.

@@

\textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
                So some of the vulnerabilities were not updated yet. For example CVE-2019-5094, which
		was published on 2019-09-24, was not 
		updated in Clair Scanner's database that time. Due to which it is missed by Clair Scanner.

\textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when package’s version have epoch 
		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.

\textbf{With CVE status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

@@

\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find package manager inside the image and then update the image according the package manager it finds.
When these images are rescanned after updation, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
till date so there is nothing that can be done to remove these vulnerabilties. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2} shows number of vulnerabilities that are detected by Anchore after updating these images.

>>>>

Tools that are capable of packing and running an application in an isolated environment
are known as container tools. Alongwith an application, they also pack the application's dependencies,
required libraries and configuration files for the
application to function properly. The functioning of an application in an isolated environment
is called a container. Containers directly run on the Host machine's kernel so they are lightweight.
Consequently, more containers can be run on a given Host machine as compared to virtual machines.

@@

\textit{Docker Daemon:} It acts as a server. It is
a long-running process that manages all Docker images, containers, storage volumes, and networks.

\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
to talk to the \textit{Docker Daemon}.

@@

\begin{comment}
It is responsible for launching containers, their
isolation, and spawning shells into the containers. It is also
responsible for managing Docker images i.e \textit{pull} and \textit{push}
from image repository, building images from Dockerfiles, signing them, etc.
When a Docker container runs, the container process is spawned as a
child of this root owned daemon. 
\end{comment}
As Docker users directly interact with the
Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
If a user gets root privileges, it
introduces unthinkable security risks for multi-tenant shared
environments. Due to this reason, Docker is not supported by
HPC environments.

@@

Singularity is another tool for packing and running applications in containers. 
In our experiments, we used $2.5.2$ Singularity version. In contrast to Docker,
Singularity does not run containers as root. Consequently, users cannot escalate
privileges in Singularity containers making it suitable for HPC environments.

\begin{comment}
Singularity offers mobility of compute by facilitating portable environments 
through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
is created, it is hashed using SHA-256. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Main features provided by
Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
We used Singularity version $2.5.2$ in our experiments.
Users can easily access files, devices, sockets, ports of the host system from
the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
into the running container. Additional directories can be specified with \textit{--bind}
to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
However namespaces can be requested if required. Users cannot escalate privileges inside
Singularty containers. This is because Singularity do not run containers as root.
Instead, a user inside Singularity container is the same user outside the container.
\end{comment}

@@

A container image is a package that contains an application along with its
required dependencies and libraries.
Both, Docker and Singularity, have different image formats. Below we provide a description of both image
formats.

@@

On the other hand, a Singularity image is a single immutable file and 
does not contain layers.
Once a Singularity image is created, it cannot be changed, consequently,
it can be used for reproducing the results of scientific
experiments.
\begin{comment}
Singularity takes snapshot, locks, and archives the developed application,
which is known as Singularity image.
It means that Singularity image is a single immutable file that can be moved around as
any other file. This file can be checksummed, signed, and easily
used for verification purposes. Singularity containers use Squashfs file format
by default. It is read-only file system in Linux, which uses compression for files,
inodes, and directories. However, Singularity also supports two other 
formats i.e \textit{sandbox} format
(which is just a chroot
directory) and \textit{writable} format (the ext3 file system).
While publishing experimental results, authors can also publish Singularity
image along with its hash, which allow other researchers to verify results.
\end{comment}
\subsection{Application frameworks}

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because one of them was not available
on the Docker hub.

@@

Boutiques~\cite{glatard2018boutiques} is an application sharing system to
publish, integrate, and execute command-line applications across different
platforms. In Boutiques, the command-line of the application is described
through a flexible JSON descriptor pointing to a Docker or a Singularity
image where the application is installed. A set of core tools help
construct, validate, publish and execute Boutiques descriptors. Boutiques
applications are published on the Zenodo research repository.

We used the 49 Boutiques applications published on Zenodo at the time of
the writing. These applications use 23 different container images. Out of these images,
3 images are not found and 2 images were already included in BIDS images.
Therefore we are left with a total 18 Boutiques images which include 6
Singularity images and 12 Docker images.

@@

BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
analysis pipelines. It improves usability, accesibility, and reproducibility
of different applications through containerization.
At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
on Docker hub.

So we have a total 38 Docker images from both BIDS Apps and Boutiques.
	Table~\ref{table1} displays the names of all the images that we took in our experiments.
%\begin{figure}
%\csvreader[%
% respect all,%
%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
%      \begin{adjustbox}{max width=\columnwidth},
%  after reading=\end{adjustbox},
% tabular={c |c | c | c | c},
%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
% late after line= \\,
%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
%]{results.csv}{}{\csvlinetotablerow}%
%       \centering
%	\caption{Existing number of Vulnerabilities}
%\end{figure}

@@

BIDS app and Boutiques images that we took for our experiments have diverse Linux
distributions such as Ubuntu, Centos, Debian, and Alpine. In the case of Ubuntu, release
can be of two types: regular or LTS (Long Term Support).
Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
in the form of Extended Security Maintenance (ESM) release.
ESM is a paid service that can be requested from Ubuntu to get security 
updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
exists in LTS.

@@

Scanning an image means looking into the image, collecting all the information about the image, and
finally, using this information to detect vulnerabilities present inside the image.
Scanning can be broadly categorized into two types: \rom{1}) Static Scanning and \rom{2})
Dynamic Scanning.
In Static scanning, an image is scanned without running it into a container. In respect to that,
different image features are extracted like installed packages, their versions, files, etc.
On the other hand, Dynamic scanning involves running a container from the image and then scanning the
dynamic behavior of the image.

@@

We used three scanners namely Anchore~\cite{github_2019}, Vuls~\cite{future-architect_2019}, and
Clair Scanner~\cite{arminc_2019} for scanning Docker images because these are the most
mature scanners. Out of these scanners, only Vuls uses dynamic scanning and the remaining two
are static scanners.
Also, we froze vulnerability databases for these scanners on September 25, 2019, and scanned
all images to avoid getting different results due to the differences in the scanner's database.
Lastly, for scanning Singularity images, we used Stools.

@@

Anchore compares package versions, which are present inside the
image, with the vulnerability database to flag vulnerabilities.
To get a vulnerability feed of various OS distribution, Anchore refers to
different sources. For example, the Ubuntu launchpad database is used for Ubuntu.
In Ubuntu launchpad database, for a given CVE, there is an entry for all ubuntu releases.
Ubuntu releases are listed with the package name
in which vulnerability exists and are entitled a status
(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
encoded in the following form:
\newline \\

@@

The status can be any one of the following:

@@

\textbf{not-affected:} The package (inside the given release), while related to the
		CVE in some way, is not affected by the issue. Notes should
		provide detailed information if needed. For e.g
		"not-affected (1.14.6-1.1)" indicates that this specific
		package version in the given release is not affected.

@@

\textbf{ignored:} The package (inside the given release), while related to the
		CVE in some way, is being ignored for some reason.  The
		notes should provide that reason. For e.g "ignored (reached end-of-life)".
		This means that this given Ubuntu release already reached
		end-of-life so this CVE is ignored by Ubuntu. However, if there
		is extended security support for this release then this
		CVE will be handled in ESM release.

\textbf{pending:} The package (inside the given release) is vulnerable and
                  has been fixed but an update has not been yet uploaded or
		  published. The "version" indicates the package version 
		  that contains the fix.

@@

Figure~\ref{example} illustrates how the information of a CVE is represented
in the Ubuntu launchpad database.

@@

Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
Using a dynamic scanning technique, it offers
remote and local scans. The remote scan involves setting up only one machine, to
which other target servers are connected via SSH. Local scan involves running
the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
and deep scan.
The Fast scan is performed without root privileges, whereas a fast root scan is
performed with root privileges. The latter also uses checkrestart utility to 
detect processes that are updated but not yet restarted because if they are not
restarted, updates are not effective. So fast root scan also detects these
processes. Both fast scan and fast root scan are performed offline without Internet
access, and put almost no load on the scan target server. The Deep scan uses
root privileges for scanning and is used to get a more detailed scan. It checks
changelogs, which puts more load on the target server.
Vuls gets data from Open Vulnerability and Assessment Language (OVAL).

@@

CoreOS originally created Clair, a static vulnerability scanner for containers. 
\begin{comment}
The main goal of the
tool is to provide a transparent look of container’s security. Clair scans container images in regular
intervals, and stores metadata of vulnerabilities, after getting from configured
set of sources. 
\end{comment}	
Clair API can be used by clients to query its database to get
the list of vulnerabilities that a particular image has. Clair sends a notification
to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
provide the facility for comparing
the vulnerability list of a particular image against a whitelist of vulnerabilities that you
want to ignore~\cite{arminc_2019}. 
So, to remove
that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
that are not present in the whitelist.
Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
Whenever Ubuntu updated its database, this image is also updated with the required information.

@@

\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
for scanning Singularity images for vulnerabilities.
Initially, Clair Scanner was intended to scan Docker Containers. This tool does not fit well
to scan Singularity images because of the different image formats.
However, TravisCI and CircleCI are commonly used for testing code, and these
services also offer running containers. So Stools combined both the concepts.
It involves spinning a Clair Scanner container during testing and building a
Singularity image, and scanning it for filesystem before the image is finalized.

@@

If there exist vulnerabilities in the container image, then we can
run after updating the
image. Updating the image involves updating all software packages that are
inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
to update all images, which checks the
package manager present inside the image and then according to that it
updates the image. However, this option affects the reproducibility
of the image, which means that the image cannot be used to verify the research
findings of other scientists.

@@

In this section, we present and compare the scanning results of three scanners.

@@

Figure~\ref{fig:venn} illustrates the number of vulnerabilities detected by scanners. The
overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
three scanners. In total 10691 vulnerabilities are detected by three scanners.
There are also vulnerabilities that are detected only by one scanner.

Figure~\ref{fig:graph1} gives more image-specific information.
It represents the number of vulnerabilities that are present inside images.
The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
also get increased.
The figure also infers that Alpine distribution, being the
lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.

@@

Table~\ref{table1} compares the results of scanning images with the three scanners.
Venn Diagram in Figure~\ref{fig:venn} summarizes this table.

When we add all regions of Venn diagram
we get total 20050 vulnerabilities in Bids and Boutiques images.
It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
reported by Anchore, 673 only reported by Clair, and 325 only detected by Vuls.

The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
The question arises why these scanners report different numbers and types of vulnerabilities.
How their logic differs and what exactly is making these results different than each other.

According to our investigation of these results, below are some of the reasons for
getting different results from these scanners. These reasons include bugs in scanners,
some scanners ignoring vulnerabilities in a particular package, referring to different databases,
how frequently they are updating their databases, etc.

@@

\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
whereas Anchore reports them.
4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
detected by both Vuls and Clair Scanner.

\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities with status
as "not-affected". So it means Linux distribution which is inside the image is not affected
by the particular CVE. However, it is reported by Vuls. In other words, we can say that
these are false positives by Vuls.
For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
is not affected by this CVE.

\textbf{With CVE status as "Ignored (reached end-of-life)":}
Some vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
only refers to ESM release. On the other hand, if the vulnerability
status in ESM release is "DNE" (Does Not Exist), then Clair Scanner will not report it. 
For example CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
release so Clair Scanner also does not report it. As Ubuntu 14.04 LTS release is present inside the images still
Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.

@@

\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
is present in package Cairo in Xenial release and it is not detected by Clair.

@@

\textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
                So some of the vulnerabilities were not updated yet. For example, CVE-2019-5094, which
		was published on 2019-09-24, was not 
		updated in Clair Scanner's database that time. Due to which it is missed by Clair Scanner.

\textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
		not detected by Anchore. This bug gets triggered when a package’s version have epoch 
		(1:3.3.9-1ubuntu2.3) in it. For example, CVE-2018-1125 in Procps package is not
		detected by Anchore due to the presence of epoch in the Procps package version.

\textbf{With CVE status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
		For example CVE-2019-13565 in Ubuntu 14.04.

@@

\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of other CVEs. 
	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753.

@@

The next experiment involves updating all these images and then rescanning them to see how the number of
vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
will find the package manager inside the image and then update the image according to the package manager it finds.
When these images are rescanned after the update, results changed drastically. However, there are still
vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
to date. There are only two
options, either you accept those vulnerabilities and use that image, or you discard that image.
So one thing is clear here that even if we keep our images up to date there will be still some
vulnerabilities that we have to face.
Figure~\ref{fig:graph2} shows the number of vulnerabilities that are detected by Anchore after updating these images.
